An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures

### 2021-04-01 CMPSpaper_writing/CMPSpaper_writing.Rmd
couple of edits

```{r, echo=FALSE, out.width="300px", fig.cap="The dark grey line shows the comparison profile; each red line segment shows one comgruent matching profile segment. "}
knitr::include_graphics("img/sigplot1.png", dpi = 100)
```

@@

```{r, echo=FALSE, out.width="300px", fig.cap="The dark grey line shows the comparison profile; the red line shows the reference profile. Solid part is the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position. "}
knitr::include_graphics("img/sigplot2.png", dpi = 100)
```

>>>>

```{r, echo=FALSE, out.width="300px", fig.cap=" \\hh{I don't think we need fig 3 when we have fig 4 XXX} The dark grey line shows the comparison profile; each red line segment shows one comgruent matching profile segment. "}
knitr::include_graphics("img/sigplot1.png", dpi = 100)
```

@@

```{r, echo=FALSE, out.width="300px", fig.cap="  \\hh{ Could you make the cnsidered segments visible, maybe by zebra-striped rectangles in the background? XXX} The dark grey line shows the comparison profile; the red line shows the reference profile. Solid part is the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position. "}
knitr::include_graphics("img/sigplot2.png", dpi = 100)
```
